On the discovery of K-enhanced and Mg-depleted stars throughout the Milky Way\footnote{This paper includes data gathered with the 6.5 meter Magellan Telescopes located at Las Campanas Observatory, Chile.}

### 2018-02-20 article/ms.tex
more comments, deleted kobayashi galaxy references in favour of APOGEE, changed graph

Beyond the intrinsic scientific value of identifying the responsible mechanism for the puzzling Mg--K anti-correlation, a satisfactory explanation for the Mg--K signature may also offer insight into the underestimation of K abundances in the Milky Way predicted by Galactic chemical evolution models \citep{kobayashi2011} or more broadly help to understand globular cluster formation and evolution. Here we use \lamost\ data to conduct the largest search to date for stars enhanced in potassium and depleted in magnesium. The discovery (or non-discovery) of such stars guides models that attempt to explain the Mg--K anti-correlation and related abundance phenomena. In particular, such a search provides strong evidence either for or against the uniqueness of the progenitor stars to globular clusters. In Section \ref{sec:method} we outline our methods to identify candidates enhanced in K and depleted in Mg, and the follow-up observations and abundance analysis for some of those candidates. In Section \ref{sec:discussion} we discuss our results and their implications for possible pollution mechanisms. Section \ref{sec:conclusion} summarises those results.

@@

We fit a Gaussian profile to the flux residuals for all three absorption lines in the Mg triplet (5167\,\AA, 5172\,\AA, 5184\,\AA) as well as the K doublet (7665\,\AA, 7699\,\AA) for all \LamostGiants\ giants. For each star we recorded the profile amplitudes, wavelengths, widths, as well as associated measurement uncertainties of these quantities. We note that although telluric absorption would usually swamp the K doublet lines, the contributions of telluric features have been removed from \lamost\ spectra as part of the data reduction process conducted by \lamost \citep{luo2016vizier}. We identified candidates by requiring that they match at least one of the following three quality filters:
\begin{enumerate}
\item We required the amplitude $A$ of the profile at the Mg 5184 \AA \ line to satisfy $A_{{\rm Mg} @ 5184} > 0.05$ and the amplitude of the profile at the K 7665\,\AA\ line to satisfy $A_{{\rm K}\,@\,7665} < -0.05$. Both amplitudes must also be measured at more than $3\sigma$ ($|A|/\sigma_{A} \geq 3$).
\item We required any two of the three Mg triplet lines to satisfy $A > 0.05$ and at least one K line to have $A < -0.05$, and for those amplitudes to have $|A|/\sigma_{A} \geq 3$.
\item We required any two of the three Mg triplet lines to have $A > 0$ and both K lines to have $A < 0$, and for the spectra to have a signal-to-noise ($S/N$) ratio of $S/N > 30$ in \lamost and a reported $\chi_{r}^2 < 3$ from \tc.
\end{enumerate}

@@

@@

\begin{figure}
	\includegraphics[width=\columnwidth]{KvsMg.png}
    \caption{Comparison of [K/Fe] vs [$\alpha$/Fe] for the candidate stars with [K/Fe] vs [Mg/Fe] abundances for NGC 2419 and NGC 2808 \citep{cohenkirby2012, mucciarelli2012, mucciarelli2015}. See text for discussion on the use of [$\alpha$/Fe] as a proxy for [Mg/Fe].} 
    \label{KvsMg}
\end{figure}

@@

\subsection{Association with known globular clusters}
\label{sec:globclustasoc}
We cross-matched our candidates with the positions of all known globular clusters \citep{harris1996}. No candidates can be associated with NGC~2419 or NGC~2808. The closest candidate to any star cluster is J074807.22+261514.2, which lies 2.54\degree\ from Ko~2 \citep{koposov2007}. The large angular separation and relatively  high metallicity of J074807.22+261514.2 ($[{\rm Fe}/{\rm H}] = -0.24$) make it highly unlikely to be associated with Ko~2.

@@

Abundance ratios of [$\alpha$/Fe] in our sample fall within the lower limits for [Mg/Fe] of the Mg-normal population of both NGC 2419 and NGC 2808, although as we are unable to decouple [Mg/Fe] from $[\alpha$/Fe], the exact level of Mg depletion of the candidates is unclear. The [Mg/Fe] abundances derived from Magellan/MIKE's high resolution spectra are consistent with the Mg-normal population in NGC 2419. However, the \lamost\ spectral flux residuals with \tc\ model are consistent with an under-abundance of Mg. The small sample of stars for which we have high resolution spectra, coupled with the conflict with the \lamost\ spectra, means we are unable to confidently make a statement regarding the level of [Mg/Fe] compared to NGC 2419 or NGC 2808.

Given that the sample is almost certainly comprised of disk stars, it is relevant to also compare with typical Galactic abundances for [K/Fe], taken from \cite{kobayashi2011}. The sample's [K/Fe] appears definitively anomalous, with Galactic [K/Fe] around $0.3 \pm 0.2$\,dex, while the identified candidate stars have a spread in [K/Fe] of 0.8 to 1.3. Note that the Magellan/MIKE abundance for candidate star J091825.49+172114.5 has [K/Fe] $=1.54$, confirming that at least some of the sample stars have extremely high levels of [K/Fe], approaching the extreme levels observed in NGC 2419.

@@

Suppose some unknown event unique to very metal-poor (possibly zero-metallicity) environments occurs that results in a gas cloud depleted in Mg and enhanced in K. The stars that form directly from this gas display a significant reduction in Mg and enhancement in K abundances similar to NGC 2419's extreme population. We will refer to this generation of stars as Generation 1\footnote{Reluctantly.}. When the most massive stars of Generation 1 die, they release metals into the gas cloud, including significant amounts of Mg, which is formed in copious amounts in core-collapse supernovae, but \textit{not} K, which models predict to be very difficult to form in significant quantities. The [Mg/Fe] depletion originally carried in the cloud is much harder to detect in the next generation (Generation 2) of stars forming from this material, owing to the influx of Mg-rich material released by Generation 1. However, the K enhancement remains relatively easy to detect, having only been reduced relative to [Fe/H] by the total amount of iron released. As this cycle repeats, [K/Fe] falls in each successive generation of stars, while the original [Mg/Fe] depletion quickly becomes impossible to detect in all but the most metal-poor stars. This cycle allows for the Mg depletions to be preserved in globular clusters, in which even the most massive clusters only form at most two generations of stars, while the signature would be lost in the disk of the Galaxy where many generations of stars form. Thus it provides a way of linking the current observations of our 112 candidate stars with the observations of NGC 2419. 
%Certainly the idea that both groups of anomalous stars arise from the same polluter source ought to be entertained.

@@

%An intriguing anti-correlation between [K/Fe] and [Fe/H] is observed, although whether or not this relation is physical remains uncertain without further higher resolution observations of the candidates. Further high resolution observations r
will also allow Mg and other elemental abundances to be determined.

>>>>

Beyond the intrinsic scientific value of identifying the mechanism responsible for the puzzling Mg--K anti-correlation, a satisfactory explanation for the Mg--K signature may also offer insight into the underestimation of K abundances in the Milky Way predicted by Galactic chemical evolution models \citep{kobayashi2011} or more broadly help to understand globular cluster formation and evolution.

Here we use low resolution \lamost\ data to conduct the largest search to date for stars enhanced in potassium and depleted in magnesium. The discovery (or non-discovery) of such stars guides models that attempt to explain the Mg--K anti-correlation and related abundance phenomena. In particular, such a search provides strong evidence either for or against the uniqueness of the progenitor stars to globular clusters. In Section \ref{sec:method} we outline our methods to identify candidates enhanced in K and depleted in Mg, and the follow-up observations and abundance analysis for some of those candidates. In Section \ref{sec:discussion} we discuss our results and their implications for possible pollution mechanisms. Section \ref{sec:conclusion} summarises those results.

@@

We fit a Gaussian profile to the flux residuals for all three absorption lines in the Mg triplet (5167\,\AA, 5172\,\AA, 5184\,\AA) as well as the K doublet (7665\,\AA, 7699\,\AA) for all \LamostGiants\ giants. For each star we recorded the profile amplitudes, wavelengths, widths, as well as associated measurement uncertainties of these quantities. We identified candidates by requiring that they match at least one of the following three quality filters:
\begin{enumerate}
\item We required the amplitude $A$ of the profile at the Mg 5184 \AA \ line to satisfy $A_{{\rm Mg} @ 5184} > 0.05$ and the amplitude of the profile at the K 7665\,\AA\ line to satisfy $A_{{\rm K}\,@\,7665} < -0.05$. Both amplitudes must also be measured at more than $3\sigma$ ($|A|/\sigma_{A} \geq 3$).
\item We required any two of the three Mg triplet lines to satisfy $A > 0.05$ and at least one K line to have $A < -0.05$, and for those amplitudes to have $|A|/\sigma_{A} \geq 3$.
\item We required any two of the three Mg triplet lines to have $A > 0$ and both K lines to have $A < 0$, and for the spectra to have a signal-to-noise ($S/N$) ratio of $S/N > 30$ in \lamost and a reported $\chi_{r}^2 < 3$ from \tc.
\end{enumerate}

@@

We note that although telluric absorption would usually swamp the K doublet lines, the contributions of telluric features have been removed from \lamost\ spectra as part of the data reduction process conducted by \lamost\ \citep{luo2016vizier}. Subsequent examination the radial velocities for the (manually vetted) sample showed no behaviour indicating that the [K/Fe] over-abundances identified were due telluric absorption.

@@

\begin{figure}
	\includegraphics[width=\columnwidth]{KvsMg.png}
    \caption{[K/Fe] vs [$\alpha$/Fe] for the candidate stars, overlaid with [K/Fe] vs [Mg/Fe] abundances for NGC 2419 and NGC 2808 \citep{cohenkirby2012, mucciarelli2012, mucciarelli2015}. See section \ref{sec:method} for discussion on the use of [$\alpha$/Fe] as a proxy for [Mg/Fe].} 
    \label{KvsMg}
\end{figure}

@@

\subsection{Association with known globular clusters}
\label{sec:globclustasoc}
We cross-matched our candidates with the positions of all known globular clusters \citep{harris1996}. No candidates can be associated with NGC~2419 or NGC~2808. The closest candidate to any star cluster is J074807.22+261514.2, which lies 2.54\degree\ from Ko~2 \citep{koposov2007}. This separation implies a minimum 1.77\, kpc distance from Ko 2, while Ko 2 has an estimated size of around 3\, pc \citep{koposov2007}.

@@

Abundance ratios of [$\alpha$/Fe] in our sample fall within the lower limits for [Mg/Fe] of the Mg-normal population of both NGC 2419 and NGC 2808, although as we are unable to decouple [Mg/Fe] from $[\alpha$/Fe], the exact level of Mg depletion of the candidates is unclear. The [Mg/Fe] abundances derived from Magellan/MIKE's high resolution spectra are consistent with the Mg-normal population in NGC 2419. However, the \lamost\ spectral flux residuals with \tc\ model are consistent with an under-abundance of Mg. The small sample of stars for which we have high resolution spectra, coupled with the conflict with the \lamost\ spectra, means we are unable to confidently make a statement regarding the level of [Mg/Fe] in our sample.

Given that the sample is almost certainly comprised of disk stars, it is relevant to also compare with typical Galactic abundances for [K/Fe], taken from the APOGEE survey \citep{alam2015} and shown in Figures \ref{KvsMg} and \ref{KvsMg}. The sample's [K/Fe] appears definitively anomalous, with Galactic [K/Fe] around $0.3 \pm 0.2$\,dex, while the identified candidate stars have a spread in [K/Fe] of 0.8 to 1.3. Note that the Magellan/MIKE abundance for candidate star J091825.49+172114.5 has [K/Fe] $=1.54$, confirming that at least some of the sample stars have extremely high levels of [K/Fe], approaching the extreme levels observed in NGC 2419.

@@

Suppose some unknown event unique to very metal-poor (possibly zero-metallicity) environments occurs that results in a gas cloud depleted in Mg and enhanced in K. The stars that form directly from this gas display a significant reduction in Mg and enhancement in K abundances similar to NGC 2419's extreme population. We will refer to this generation of stars as Generation 1. When the most massive stars of Generation 1 die, they release metals into the gas cloud, including significant amounts of Mg, which is formed in copious amounts in core-collapse supernovae, but \textit{not} K, which models predict to be very difficult to form in significant quantities. The [Mg/Fe] depletion originally carried in the cloud is much harder to detect in the next generation (Generation 2) of stars forming from this material, owing to the influx of Mg-rich material released by Generation 1. However, the K enhancement remains relatively easy to detect, having only been reduced relative to [Fe/H] by the total amount of iron released. As this cycle repeats, [K/Fe] falls in each successive generation of stars, while the original [Mg/Fe] depletion quickly becomes impossible to detect in all but the most metal-poor stars. This cycle allows for the Mg depletions to be preserved in globular clusters, in which even the most massive clusters only form at most two generations of stars, while the signature would be lost in the disk of the Galaxy where many generations of stars form. Thus it provides a way of linking the current observations of our 112 candidate stars with the observations of NGC 2419. 
%Certainly the idea that both groups of anomalous stars arise from the same polluter source ought to be entertained.

@@

%An intriguing anti-correlation between [K/Fe] and [Fe/H] is observed, although whether or not this relation is physical remains uncertain without further higher resolution observations of the candidates. Further high resolution observations will also allow Mg and other elemental abundances to be determined.
